(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned it's a Working Title.

### 2015-02-24 ms.tex

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\project}[1]{\textsl{#1}} 
\newcommand{\kep}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}

@@

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we employ the use of two stellar models. 
We first download the isochrone grids from the 2012 updated photometric
systems for the relevant bandpasses from the Dartmouth Stellar Evolution
Database \citep{Dotter08}. 
We then interpolate the isochrones onto a grid uniformly spaced in
stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to 
\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to 
1000 pc). 
In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
We then compare the expected apparent magnitudes to our observed photometry
to measure the likelihood of each grid point.
For each parameter, we then marginalize our likelihood over all other 
parameters in order to estimate the value of the physical properties
for each star.

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we remain ignorant of any systematic uncertainties that may be
induced by our reliance on the Dartmouth models.
To this end, we repeat this procedure with the Padova database of stellar
evolutionary tracks and isochrones \btmtodo{Cite: Who? Claims to be in
file headers}. 
Comparing two models will not help us understand any systematic errors
of the two are biased in the same way, but in general it will allow us
to calculate a more accurate assessment of our true uncertainties than 
relying on one model alone.

\subsection{SpeX Spectroscopy}

@@

@@

\bibliography{exopapers}

>>>>

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\project}[1]{\textsl{#1}} 
\newcommand{\kep}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand\teff{\ensuremath{T_\text{eff}}}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}

@@

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we employ the use of stellar models. 
We first download the isochrone grids from the 2012 updated photometric
systems for the relevant bandpasses from the Dartmouth Stellar Evolution
Database \citep{Dotter08}. 
We then interpolate the isochrones onto a grid uniformly spaced in
stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to 
\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to 
1000 pc). 
In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
We then compare the expected apparent magnitudes to our observed photometry
to measure the likelihood of each grid point.
For each parameter, we then marginalize our likelihood over all other 
parameters in order to estimate the value of the physical properties
for each star.

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may underpredict 
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}. 
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included. 
However, at the low-mass end including the WISE data systematically increases the 
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552 
(\textsection\ref{Spexobs}) suggest the derived photometric properties better 
represent the true physical parameters when the WISE data is included.

\btmtodo{Show plot}

\subsection{SpeX Spectroscopy}
\label{Spexobs}

\btmtodo{Some of Mann's references aren't in his .bib file. Fix.}

A near-infrared spectrum of EPIC 201912552 was obtained using the updated SpeX 
(uSpeX) spectrograph \citep{Rayner03} on the NASA Infrared Telescope Facility 
(IRTF) on January 29 2015 (UT). 
SpeX observations were taking using the short cross-dispersed mode and the
0.3$\times15\arcsec$ slit, which provides simultaneous coverage from 0.7 
to 2.5$\mu$m at $R\simeq2000$. 
The target was observed at two positions along the slit to subsequently subtract 
the sky background. Eight spectra were taking following this pattern, which provided 
a final S/N of $>150$ per resolving element. 
The spectrum was flat fielded, extracted, wavelength calibrated, and stacked 
using the \textit{SpeXTool} package \citep{Cushing:2004}. 
An A0V-type star was observed immediately after 
the target, which was used to create a telluric correction using the 
\textit{xtellcor} package \citep{Vacca:2003}.

An optical spectrum was obtained using the SuperNova Integral Field Spectrograph
\citep[SNIFS,][]{2002SPIE.4836...61A,Lantz:2004} on the University of Hawai'i 
2.2m telescope on the night of January 30 2015. 
SNIFS provides simultaneous coverage from 3200\AA--9700\,AA\ at a resolution 
of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element 
in the red ($\sim6000$\AA). 
Details of the SNIFS reduction, including dark, bias, and flat-field corrections,
cleaning the data of bad pixels and cosmic rays, and extraction of the 
one-dimensional spectrum are  described in \citet{Bacon:2001} and 
\citet{Aldering:2006}. 
Flux calibration was performed using a separate pipeline described in \citet{Mann2015}.

\teff\ was calculated by comparing our optical spectra with the CFIST
suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
version of the PHOENIX atmosphere models \citep{Allard:2013}, which gave a temperature
of 3503 $\pm$ 60\,K. 
More details of this procedure are given in \citet{2013ApJ...779..188M} and
\citet{2014MNRAS.443.2561G}. 
This method was used because it is known to accurately reproduce empirical 
\teff\ values from long-baseline optical interferometry \citet{Boyajian2012}.

Metallcity was determined using the procedures from \citet{Mann2013a}. 
\citet{Mann2013a} provide empirical relations between atomic features and M dwarf
metallicity, calibrated using wide binaries. 
We adopted the weighted mean of the $H-$ and $K-$band calibrations, 
which yielded a metallicity of 0.09$\pm$0.09.

We combined the derived \teff\ and [Fe/H] values with the empirical 
\teff-[Fe/H]-$R_*$ relation from \citet{Mann2015} to compute a radius. 
Accounting for measurement and calibration errors in [Fe/H] and \teff\ we calculated 
a radius 0.394$\pm0.038R_\odot$. 
We use these parameters instead of the derived photometric properties for this target.

@@

\subsection{TRES Radial Velocities}

@@

\bibliography{exopapers; mannbib}
